### 2024-11-29 paper/eval.tex
Add number

We manually craft the specification including the proposal features using the
DSL, and similarly generate a Wasm interpreter using AL.
This interpreter is tested against the execution tests in the official test
suites and the proposals, excluding test related to the infinite loop
detection.
The interpreter successfully passed all ??? execution tests, in ??? seconds.
Passing all these tests demonstrates the generality of AL.

>>>>

We manually craft the specification including the proposal features using the
DSL, and similarly generate a Wasm interpreter using AL.
This interpreter is tested against the execution tests in the proposals,
excluding test related to the infinite loop detection.
The interpreter successfully passed all 59,975 execution tests, in 2,375
seconds.
Passing all these tests demonstrates the generality of AL.
